Draft

### 2012-10-31 docs/roadmap/draft.tex
Roadmap.

\subsubsection*{Todo @TCK}
\begin{verbatim}
1. check the vanilla implementation
2. read ADP legacy parsers
3. presentation for Thursday
4. Propose an IR and code generators related to
Note. We only need to generate code directly for CUDA, no interaction. Look at string templating .
"""xxx $var xxx"""
- Fork LMS on GitHub and cleanup all the CUDA generator

>>>>

\begin{verbatim}
restrict to only 1 max/min (more restrictive than ADP)

for optimization we want to split grammar into binary productions, to do that we need
to have equality on the following formula. We can solve it more easily if functions are linear
\end{verbatim}
\[\min\limits_{i<k_1<k_2<j}\big[ f(i,k_1,k_2,j) \big] \le  \min\limits_{i<k_2<j} \big[ g_2(i,\min\limits_{i<k_1<k_2} \big[ (g_1(i,k_1,k_2  ) \big],k_2,j) \big]  \]

\begin{verbatim}
Roadmap:
2.11 Come with an IR prototype: data structures and nodes
9.11 GenScala on LMS, JNI working for arbitrary types
16.11 GenCuda + LMS CudaCompiler
23.11 Problem generalization: "cyclic keyword", Zucker problem / CudaLoop optimization
30.11-- Gap due to LMS missing knowledge
7.12 Benchmarking, grammar analysis
14.12
21.12
28.12 -------
4.01 -------
11.01 writing report = implementation description + plan for future work
18.01 writing report
\end{verbatim}

\subsubsection*{Todo @TCK}
\begin{verbatim}
cleanup ADP code
4. Propose an IR and code generators related to
Note. We only need to generate code directly for CUDA, no interaction. Look at string templating .
"""xxx $var xxx"""
- Fork LMS on GitHub and cleanup all the CUDA generator
